The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-15 analysis/paper/paper.qmd
Add analysis chunk from old script

# Preview theses in increasing order of graduation year
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  head_text(head_n = 5)

# Show distribution of the length of theses
hist(str_length(emu_theses$text_clean))
```

@@

>>>>

# Preview theses
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  str_sub(1, 500)

# Preview theses
hist(str_length(emu_theses$text_clean))

Encoding(emu_theses$text_clean)
```

@@

emu_theses_bigrams_top_all <- emu_theses_bigrams %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(bigram = reorder(bigram, n))
